Water Management

### 2020-02-11 Paper/paper.tex
typos

			\textbf{Niklas Sayer} \\
			stud. 2nd semester M.Sc. Business Administration and Engineering: Materials- and Process Engineering\\
			Matr. Nr. 332404
			\href{mailto:niklas.sayer@rwth-aachen.de}{niklas.sayer@rwth-aachen.de}

@@

	Every value along the possible water level leads to a irrigation amount that optimizes the value for all users in the given situation. Summarizing these values over the range of possible water levels results in a optimal irrigation policy which is shown in figure \ref{fig:optimal-irrigation-policy}.

@@

	The result is put in a histogram and shown in figure \ref{fig:steadyStateMonteCarlo}.
	The highest possibility for a steady state is around 4.2. 
	In edge cases one can find steady states as low as 3.5 or as high as 5.2. 
	The curve resembles a normal distribution. 

>>>>

			\textbf{Niklas Sayer} \\
			stud. 2nd semester M.Sc. Business Administration and Engineering: Materials- and Process Engineering\\
			Matr. Nr. 332404 \\
			\href{mailto:niklas.sayer@rwth-aachen.de}{niklas.sayer@rwth-aachen.de}

@@

	Every value along the possible water levels leads to an irrigation amount that optimizes the value for all parties in the given situation. Summarizing these values over the range of possible water levels results in a optimal irrigation policy which is shown in figure \ref{fig:optimal-irrigation-policy}.

@@

	The result is put in a histogram and shown in figure \ref{fig:steadyStateMonteCarlo}
